### 2013-07-24 1_introduction/introduction.tex
updated for Ian changes

%: ----------------------- introduction file header -----------------------
\chapter{Introducing The Research Question}

Synthetic Aperture Radar can soon become the preferred choice for
  continous and autonomous large-scale remote surveillance solutions.
Compared to optical remote sensors, which is passive,
  active SAR sensors provides weather independent and night-inclusive operational capabilities.
Compared to other radar based active sensors, for example Real Aperture Radar (RAR),
  SAR provides a much better resolution, and larger coverage solution.
The once-limiting drawback of SAR is the high-demanding signal processing procedures,
  which is needed to process SAR images, has become obsolete,
  due to recent and quick advances in computational power  \citep{Cumming_2005_Artech}.

As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
Recent advances in computational power has made the once-limiting high-demanding signal-processing procedures, which are needed to process SAR images, obsolete \cite{Cumming_2005_Artech}.
Thus we believe, SAR will soon come to be the preferred choice for continuous and autonomous large-scale remote surveillance solutions.

Electromagnetic waves have the intrinsic nature of polarization.
Polarimetric SAR, i.e. POLSAR, extends the SAR acquisition information from the traditional single SAR channel to multi-channel polarimetric SAR data, corresponding to different combination of transmitted and received polarizations.
Early works from the radar community had focused on the theoretical introduction of scattering matrix, i.e. Sinclair matrix or Mueller matrices, for full, i.e. quad, polarimetric measurements \cite{Sinclair_1950_ProcsIRE}.
%(Sinclair, 1950), (TODO) 
These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \cite{Zebker_1991_ProcsIEEE}.

Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR, and so on, were launched.
However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes apparently as a compromise between theoretical polarimetric requirements and practical limitations.
Initially to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.
Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
In his pioneer paper in 2005, Souyris\cite{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode with the suggestion that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
Raney\cite{Raney_2006_IGARSS} showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave, via Stokes parameters, but also capable of detecting the basic target's polarimetric characters, i.e. odd or even bounce phenomena.

The extensions from single-channel SAR to multi-channel polarimetry can be considered as analogous to the advancement towards colour TV from the black-and-white days.
While the future is promising, both SAR and POLSAR suffer from speckle phenomena, which hampers the human capabilities to understand SAR images.
Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
%The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.

\section{The Research Question and the Motivation to Study}

Univariate SAR and multi-variate POLSAR data are multiplicative and heteroskedastic.
By definition, heteroskedastic noised data has its variance, and correspondingly its substractive distances,
  dependent on the main signal.
In another line of research, log transformation has been shown
  to convert the multiplicative nature of SAR data into a more familiar additive nature.
We hypothesize that   
  log-transformation also offers several consistent measures of distance in heteroskedastic SAR and POLSAR data.
This thesis aims to investigate and validate that hypothesis.

In this chapter: the main research problem and the corresponding hypothesis are explicitly stated.
The methodology section explains how the results are obtained and analyzed.
Contributions to advance theoretical knowledge are illustrated.
Towards the end of the thesis, an application illustrate how the theoretical results can be applied in future research and development activities.

Problem: speckle in SAR and POLSAR, especially its heteroskedastic nature. (new)

The motivation then is to provide a probably better understanding about the statistics of speckle. (new)

The motivation for this research then is to reconstruct high-quality grey-scale images from speckled single channel SAR data, and to visualise as colourful images the despeckled multi-channel POLSAR data.
In order to do so, the speckle effects need to be removed as much as possible from original (POL)SAR data.

Due to the random nature of speckle, speckle filtering has been put into the context of statistical estimation theory, which comprises statistical modelling and validation, estimator design and development as well as evaluation of different estimators' accuracy.
This proposed research project focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
The benefits of such a framework are many fold.
Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for a real expensive satellite imagery.
Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.

For single-channel SAR images, our initial observations and experiences indicate that the community has been oblivious to many of the negative effects of statistical heteroskedasticity manifested in the original intensity and amplitude data.
In Chapter 4, it is shown that logarithmic transformation can convert SAR's multiplicative stochastic process into a better-understood additive noise model.
Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.

%\subsection{The Research Questions}

Figure 
	\ref{fig:residual_as_noise} 
shows that: when compared with optical remote sensing images, SAR data suffers from serious degradation.
%SAR data suffers from stochastic speckle phenomena, which poses numerous challenges in human capabilities of understanding SAR images.
%Years of research in SAR signal processing has resulted in various speckle filters, all of which aims to produce better visually de-speckled gray images from the degraded SAR data.
The degraded SAR data almost invariably requires a treatment of speckle filtering to yield more comprehensible images.
Recent advances in Polarimetric SAR (POLSAR) have produced multiple channels of SAR data, which are conceptually similar to the multiple channels found in colourful optical images.
However, the stochastic effects of speckle on multivariate and correlated data is ever more eminent.
The key proposed research question is how to reconstruct clean, colorful visualization of Polarimetric Information from the new but speckled PolSAR satellites.
Towards the end of the research project, an optional extended question shall be how this extra de-speckled polarimetric information may help in the tasks of target detection and classification.

The main research question is conceptually divided into the following subsidiary questions to investigate:
% and project phases include. 
%1. How to simulate SAR and Polarimetric SAR data (quick pass, no lit review)
\begin{enumerate}
\item For single channel SAR data, the main aim would be how best to produce and quantitatively evaluate the de-speckled gray images. 
The main contributions could be that: for the first time, the PDF for the underlying back-scattering coefficient appears to be estimate-able, at least in the log-transformed domain. 
It is hoped this new knowledge may help in developing better speckle filters, especially those filters of \textit{Maximum a Posteriori} (MAP) nature.
Another possible contribution could be: how the homoskedasticity in the log-transformed domain could help to consistently evaluate the performance of different speckle-filters being applied on heterogeneous spatial variations.
%2. how the PDF of underlying back-scattering coefficient, in the log-domain, could be estimated and how this could help in improving the performance of the Maximum A Posteriori class of speckle-filters.
%The topic and the concept itself is a new topic
\item For multi-channel SAR data, the main aim would be to produce a smoothed and colourful visualisation of Polarimetric information. 
The main contributions would be a methodology to extends the results of single-channel SAR speckle filtering towards the issue of estimating the off-diagonal elements in polarimetric covariance matrix. 
Another fundamental contribution could be: how to model, simulate and visualize the multivariate and correlated channels in POLSAR data.
\item The third portion of this project is to investigate how full polarimetric information could be reconstructed from partial polarimetry modes. 
The main aim of this section is to fill the gap between practical dual-polarimetric implementations and theoretical established full polarimetric results. 
%The practical application is synchronized with current satellite hardware deployments and trade-offs.
\item An optional collaborative portion is to investigate how the extra information in different polarimetric modes may help in the task of target detection and classification. 
The main aim of this stage is to demonstrate the capability of (partial) polarimetric information over traditional single-channel SAR data.
%and also to evaluate the trade-off between higher resolution offered by partial polarimetric architecture and the more complete full polarimetric mode.
%Algorithms may have been and will also be proposed to tackle these issues, but the need to evaluate the algorithms requires rigorious ground-truthed data.
\end{enumerate}

%For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
%We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
%Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
%Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
%Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
%Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.

\section{Objectives, Methodology and Contributions}

\subsection{The Research Objectives}

The purpose of this section is to illustrate the objectives in developing computational frameworks for Stochastic Polarimetric Data. 
Assuming the framework will be implemented successfully, this section also describes its academic contributions as well as its projected practical benefits.
% for the industry.
%Also the academic contribution as well as practical benefits, assuming the frameworks is developed that meet the requirements, is to be described.

%Even though the research topics appears segmentable into different sub-fields, the fact is that all of them can be considered as an application of statistical estimators.
Even though the research topic spreads across different sub-fields, a common thread that bind them all together is the application and development of statistical estimators.
For single channel SAR, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
In the case of multi-channel SAR, it is the estimation of a target's polarimetric signature, being measured in multiple channels simultaneously and stochastically.
And for the problem of target detection or classification, it is the likelihood estimation that the target belongs to a certain category.
% which is then fed into a decision rule to make a last judgement.

Thus, the main objective of this research is to derive effective statistical estimators for the reconstruction and classification of the underlying target information in speckled SAR and POLSAR data.

In order to design and evaluate effective estimators, we centre our effort on developing a good computational framework. 
The objective of such framework being:
\begin{enumerate}
\item To build, develop and validate statistical models for different stochastics processes that are inherent within the polarimetric SAR domain.
\item To allow easy, fast and repeatable simulations and experiments of various stochastic processes in designed, focused, as well as broad-based scenarios.
\item To allow easy application of different existing estimators as well as various transformations into focused and simulated scenarios as well as into practical real measured data.
\item To allow development and calculation of good performance indices for estimators. 
\item To allow visualization and analysis of the performance of different stochastic estimators.
\item Ultimately, to allow development of better and more accurate estimators, whose results can be verified: not only qualitatively on real life images, but also quantitatively through rigorous simulations.
%quantitatively in rigorious simulations and qualititatively in real measured data.
\end{enumerate}

The possible benefits of the research project are:
\begin{enumerate}
\item Practical benefits
\begin{enumerate}
\item The computational frameworks allow for faster, quicker and more focused experiments. 
Often, a statistical hypothesis can be observed or rejected by designing and implementing an appropriate computational experiment.
\item The framework allows for easier analysis, and thus more insight to be gained, on the performance of an estimator. 
This, in turn, allows for design and development of better estimators.
\item Our research to find evidence, and hopefully rigorous proofs, supporting the advantages of (partial) polarimetric SAR implementations over conventional SAR data also yields high practical interest.
%Our research to find evidence, and hopefully rigorious proofs, supporting the advantanges of A over B also yields high practical interests.
%Our intended research to address a pressing practical trade-off, between a choice of better resolution and an option of complete polarimetric information, also yields high practical interests.
Apparently the topic has also received a fair share of attention and supports from EADS \footnote{This PhD research project is run in conjunction with EADS and has an EADS co-supervisor}.
\item The investigative research of ship monitoring using polarimetric SAR satellites is also apparently of high interest to EADS, as evidenced by their own in-house investigations.
\end{enumerate}
\item Academic benefits
\begin{enumerate}
\item The computational framework allows for quantitative evaluation and comparison of estimators.
With fast and repeated experiments, the framework allows one to not only compute a single performance value on a single experiment, but also to analyze the whole behaviour of such performance measures over repeated stochastic simulations.
\item For the sub-topic of single-channel SAR imagery, we believe an estimate for the PDF of the true underlying coefficient will be an unique research result.%is the first of such kind.
\item For the multi-channel POLSAR sub-field, we believe our proposed approach in speckle filtering of the off-diagonal elements in the polarimetry covariance matrix is also a novelty.
\item For the specific application of ship detection and classification, we believe our approach of evaluating the performance of higher-resolution and partial polarimetry modes using ground truth from AIS data is also unique.
\end{enumerate}
\end{enumerate}

As a testament on the effectiveness of this research, the work discussed in this report was published as two separate papers in 2010, at ISCCSP\cite{Le_2010_ISCCSP} and ACRS\cite{Le_2010_ACRS}.

\subsection{Research Methodology}

As the speckle phenomena is stochastic in nature, speckle filtering has been put into the framework of statistical estimation.
This project's research methodology will be based extensively on a statistical estimation framework. 
The framework consists of three stages:

\begin{enumerate}
\item Stage 1: data statistical analysis. 
We aim to propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
The statistical models built after such a transformation are validated against real-life data.
\item Stage 2: predictor and estimator development.
Various statistics based computational intelligence and/or signal processing methods are intended to be applied. 
\item Stage 3: results analysis and performance evaluation.
Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
%Stochastic simulation based experiments with evaluation being both through consistent quantitative measures and visual qualititative comparisions from real captured imagery. 
\end{enumerate}

\subsubsection{Data Collection}

We have used, and plan to keep using simulated data extensively. 
There appears to have a number of advantages in using simulated experiments:
\begin{enumerate}
\item Once the model is validated against real-life data, simulated experiments can be carried out on more focused scenarios.
This allows smaller data sets to be generated and analysis can become faster and more accurate.
%Experiments can be carried out on smaller scale data, with validation from real images to come later
\item Contrary to real-life images where underlying coefficients are to be estimated, ground truth is readily available in simulated experiments.
\item Quantitative evaluation is possible not only via a single experiment on a single real-image but via repeated stochastic runs. 
\item Thus not only single values of mean or mean-squared-error is to be evaluated. 
As the whole response PDF is available, statistical bias or heteroskedasticity can also be reported.
%But also statistical bias or heteroskedasticity can be estimated as the whole pdf distributions are available. 
\end{enumerate}

Besides simulated  data, we have gathered a large amount of real-life data.
The table below lists data made available to us, courtesy of EADS Innovation Works Singapore. %(TODO:RECOLLECT)

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Radar Platform & Polarization Mode & Data Capture Time \\
\hline
RadarSat 2 & Full Quad Pol & 29 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 05 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 12 Mar 2009 \\
RadarSat 2 & Full Quad Pol & 23 Jan 2009 \\
RadarSat 2 & Full Quad Pol & 30 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 06 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 19 Oct 2008 \\
RadarSat 2 & Full Quad Pol & 12 Nov 2008 \\
RadarSat 2 & Full Quad Pol & 25 Sep 2008 \\
TerraSar-X & Dual Pol (HH-VV) & 18 Apr 2008 \\
NASA-JPL AirSar & Full Quad Pol & 2001 \\
\hline
\end{tabular}

\label{tbl:collected_data}
\caption{Collected imagery data}
\end{table}

Furthermore, for the task of ship detection and classification using polarimetric data, we intended to capture ship's location using readily available Automatic Identification System (AIS) systems. 
The data collection strategy will be synchronized tasks of satellite imagery and AIS data capture.
AIS data, in a close-to-port environment, will be used as ultimate ground truth to evaluate different target detection and classification algorithms.

\subsubsection{Result Interpretation and Evaluation}

Simulated experiments allows evaluation of estimators against ground-truth.
Errors can be quantitatively analyzed and methods to reduce such errors can be developed.
Thus simulated experiments could produce quick results, which may provide faster analysis and further insights for developing more accurate estimators.

Practically in the end, all estimators would always need to be applied on real images.
Contrary to experiments on simulated data, experiments on real images can only be compared qualitatively.
This however, is critical and will always be used in our investigations.
The reason is that this helps to guard against any systematic errors in the used assumptions and approximations made in developing the theoretical models.
Towards that end, real-data can help to build and validate statistical models.

%In fact, we could build and validate statistical model for all elements of POLSAR data.
%One steps further and we could demonstrate the methodology for target detection and classification in dual-pol data.
%The original results in reconstruction from CP to FP could be revised and evaluation may be on estimates of Entropy, Polarization angle, Anisotropy (Cloude).

>>>>

%: ----------------------- introduction file header -----------------------
\chapter{Introduction}

%What is the situation, the background context of your research? the BIG problem!
Synthetic Aperture Radar is a technology with many advantages.
%Compared to optical remote sensors, which are passive, active SAR sensors provide weather independent and night-inclusive operational capabilities.
Compared to optical remote sensors - which are passive, SAR uses active sensors to provide weather independent and night-inclusive operational capabilities. 
Compared to other radar based active sensors,
for example Real Aperture Radar (RAR), SAR provides state-of-the-art resolution
and coverage.
In the past decades, the exponential growth in computational power has made the once overly excessive computationally demanding SAR technology to become a feasible and preferred earth observation solution \cite{Cumming_2005_Artech}.
Thus SAR has now become the preferred choice for continuous and autonomous large-scale
remote surveillance solutions.

As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is polarimetric SAR or POLSAR. POLSAR is the natural
extension from SAR, exploiting the natural polarization property of Electromagnetic
(EM) waves. It extends the SAR acquisition information from the traditional single
SAR channel to multi-channel polarimetric SAR data, corresponding to a different combination of transmitted and received polarizations. Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
multi-channel POLSAR data as compared to the traditional one-channel SAR data.

With both SAR and POLSAR data becoming cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. However, both SAR 
and POLSAR suffer from speckle phenomena, which hampers the human capabilities
to understand SAR images. Speckle arises due to the random interference of many
de-phased but coherent backscattered waves. Thus both SAR and POLSAR data are
stochastic by nature.

\section{Research Motivation}

%Given the BIG problem, Why it is important to solve this problem?
The
                big picture, as introduced above, is that POLSAR data is multi­dimensional,
                stochastic, multiplicative and heteroskedastic.
%Under
%                this context, the motivation is to gain a better
%                understanding of the data,
%which
%                hopefully will lead to better information that can be
%                extracted from these data.
Under this condition, it is very important to understand the statistical models for SAR
data. It is these models that form the foundation for different SAR data processing
techniques, for example speckle filtering, target detection, image segmentation, and
other clustering, classification techniques.
In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
which comprises statistical modeling and validation, estimator design and development
as well as evaluation of different estimators’ accuracy. And central to this statistical
estimation theory is the need for statistically consistent discrimination measures which
are commonly derived from the statistical models.

That is, while different statistical models have been developed for different POLSAR
observables, for a statistical model to be useful, scalar discrimination measures need to
be derived from it. At the same time, the extension from SAR to POLSAR brings about
a representation difficulty in that: there exists not one, like the intensity in SAR, but
many observable quantities in POLSAR. Thus on the one hand, practical application for
POLSAR data processing requires the measure to be scalar, consistent and preferably
homoskedastic. On the other hand, the observable quantity being modeled needs to
be naturally representative of the high dimensional POLSAR data.

%Solving these dual-problem is both important and interesting.
%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data. % dear Ian I changed this back 
%of the Additive White Gaussian Noise (AWGN) model in natural processes.
%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive. However this is definitely not true - your POLSAR data is digital and yet is not additive. Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
It should be noted that even for the case of SAR data which is digital and not additive,
  the above statement is still true as SAR actually has two components, real and imaginary part,
  and all of them follows the standard Additive White Gaussian Noise model.

Both SAR and POLSAR data however is multiplicative and heteroskedastic by nature.
While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility. 
An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
Such use, however, is known to be not very robust for these so-called heavy tailed distributions.

Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

Furthermore, since POLSAR can be considered as the multi-dimensional extension of
traditional SAR, a common problem exists for both SAR and POLSAR data. That
is: the sense of subtractive distance is seriously flawed in the original multiplicative
and heteroskedastic domain of both types of data. 
In contrast, the digital technologies which range from image processing and display to artificial intelligence and machine learning algorithms used to process (POL)SAR data are linear
and additive in nature. 
This linear and additive nature is manifested, for example, in a
large number of algorithms in the field of computational intelligence which make use of
MSE as an objective function, as well as the extensive use of variance and
contrast in digital image processing. 
Thus it is very exciting to derive homoskedastic models for this heteroskedastic data
  so that the benefits of an additive and homoskedastic statistical estimation framework can be explored.

%Specifically, 
%  this thesis focuses on providing a solution for the
%                dual-problem of: 1) developing scalar and
%                representative statistical models for the
%                multi-dimensional and inter-correlated POLSAR data and
%                2) establishing at consistent measures of distance for both
%                SAR and POLSAR data which allow the benefits of the
%                homoskedastic statistical estimation framework to be
%                demonstrated.

\section{Research Objective}

%The research objectives 
%helps to 1) define and focus your effort, 2) identify variables to be measured 3) identify steps to be performed 4) establish the limits of the study 5) avoid any data collection, argument development that is not necessarily needed.
%Should be stated in action verbs specific enough to be measurable. Avoid vague, non-active verbs which is hard to evaluate if the objectives have been achieved.
%4. Research methodologies (How the research is/was/will be conducted)
%5. Result interpretation and evaluation (describe how the results is expected to look like, how they are going to be evaluated

%How do others solve this problem?
%Briefly What are their solution? what problems they cannot yet solve?
While
                the statistical model for SAR is quite well understood,
the
                understanding of the POLSAR statistical model trails behind.
The
                complex POLSAR data have been statistically modelled as
                following the complex Wishart distribution, which
                apparently is multi­dimensional, complex and
                un­intuitive.
There
                has been a few published scalar statistical models for
                POLSAR, but none of them fit the dual criteria of being
                highly representative of the data and at the same time
                lead to scalar discrimination measures.
There
                are also a few POLSAR discrimination measures proposed,
                but all of them are based on the likelihood test
                statistics, which so far have only shown to be based on an
                asymptotic distribution.

 In
                another thread of study, to combat the negative
                impacts caused by multiplicative and heteroskedastic
                properties for SAR data, experienced researchers of the
                field have developed numerous ingenious ways to tackle
                these issues.
For
                example, when the sense of subtractive distance is not
                consistent for SAR data, the ratio is proposed as its
                discrimination measure \cite{Rignot_1993_TGRS_896}.
Or
                when the MMSE criteria is not very suitable to evaluate
                SAR speckle filters, other criteria likes radiometric
                preservation and speckle suppression power evaluation
                are employed. 
Unfortunately,
                these counter­intuitive measures are not very popular
                outside the SAR community, and newcomers to the field
                are frequently found being trapped in these pitfalls.

%In what way is your solution different ? What is the novelty in your approach and hence solution?
Some of the problems described above have been studied using different approaches in the literature.
However, the set of problems has not been presented in a systematic manner nor with a strong underlying foundational theory.
In
                this thesis, the statistical model for the determinant
                of the POLSAR covariance matrix is proposed and
                validated.
Out
                of many different possible scalar projections of the
                multi-dimensional data, the proposed projection is
                highly representative.
When the dimension number is collapsed to one, the
                special case of the proposed model matches perfectly
                with the commonly used statistical model for SAR
                intensity.
Furthermore,
                the proposed statistical model also leads to the
                derivation of existing as well as the newly proposed
                discrimination measure: determinant-ratio which is the
                generalized multi dimensional version of the widely used
                SAR intensity ratio.

 Another
                novelty of the contributions in this thesis comes from the systematic
                treatment towards the problem of statistical estimation
                of heteroskedastic SAR data.
While
                many different ways to combat the negative impacts
                caused by multiplicative and heteroskedastic properties
                for SAR data have been proposed over the years, they have often been
                handled in a piecemeal manner.
Here,
                a systematic homoskedastic framework of statistical
                estimation is developed, where not only homoskedastic
                statistical models are proposed, the impacts of
                homoskedasticity on estimator development and
                performance evaluation of statistical estimators is also
                studied.
This
                comprehensive treatment not only explains why the
                original SAR data requires special treatment very
                different to the common practice of computational
                sciences, 
it
                also allows thorough and unique discussion, for example on
                evaluating different evaluation criteria for statistical
                estimators.  % ;-)).
And
                since the POLSAR data can be considered as the multi
                dimensional extension of traditional SAR data, these
                treatments are shown extensible towards POLSAR data
                which is definitely yet another novelty.

%precise problem statement
With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
That is
                this thesis focuses on providing a solution for the
                dual-problem of: 1) establishing scalar and
                representative statistical models for the
                multi-dimensional and inter-correlated POLSAR data and
                2) providing consistent measures of distance for both
                SAR and POLSAR data which allow the benefits of the
                homoskedastic statistical estimation framework to be
                demonstrated.

\section{Research Methodology}
%To achieve the stated objectives, what is your plan of attack? Describe How your actions are to be conducted? How your argument is developed?                
%****IVM Hai, I removed this sentence. I don't think it adds anything useful...
%The bottom up development of the research effort for this long-term study, admittedly is not as straightforward as the top down layout of the stated objectives.
The
                overall research methodology is to first focus on the
                simpler one dimensional SAR domain, and then extend the
                obtained insights and processing techniques 
towards the more complex multi dimensional
                POLSAR data domain.
%***IVM   what OPEN LOOP??? I'm not sure that this is an open loop!! Can't you just say "This is achieved when....."
This
                is achieved as the theoretical models for
                POLSAR are shown to be the multi dimensional extensions of
                the one dimensional SAR model.

The
                development of these models are based on
                rigorous statistical mathematics transformations. % and theory. 
The
                assumptions used are minimal and widely
                acknowledged for this type of data.
Then, the variable change theorem is applied to derive the statistical model for these transformed observables. %log-transformed SAR data.
The
                derived theoretical models are validated against
                real life data.
And
                the imperfect conditions found in practice (in
                comparison to the theoretical assumption) are also
                investigated, and the models are shown to be robust, capable of
                handling these imperfections.
The
                theoretical properties of these models, as well as many
                of their benefits, are also proven using rigorous
                mathematical principles.

%The theoretical statistical models are derived from the commonly used statistical models for SAR and POLSAR.
%Then, as mentioned above, the variable change theorem is applied to derive the statistical model for log-transformed SAR data.
%A similar methodology is then followed for the multi-dimensional POLSAR data.
%The POLSAR theoretical foundation used is the Complex Wishart distribution applicable on the covariance matrix.
%In this thesis, the statistical model for the determinant of this covariance matrix,
%  is derived from this foundation.
%The variable change theorem is again applied to derive the discrimination measures from these derived basic models.

As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering has been put into the framework of statistical estimation.
For such application, the research methodology is based extensively on the statistical estimation framework. 
The framework consists of three stages:

%***IVM Hai, I changed your list type to make it look better
\begin{description}
\item{Stage 1:} data statistical analysis. 
We propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
The statistical models built after such a transformation are validated against real-life data.
\item{Stage 2:} predictor and estimator development.
Various statistics-based computational intelligence and/or signal processing methods are to be applied. 
\item{Stage 3:} results analysis and performance evaluation.
Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
\end{description}

\subsection{Statistical Estimation Framework for (POL)SAR data}

Even though the research topic seems to spread across different sub-fields, the common framework that binds them all together is the application and development of statistical estimators.
For speckle filtering, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
For the problem of target detection or classification,
  it is the estimation of the likelihood that the target belongs to a certain category.

Thus a significant portion of this research effort focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
The benefits of such a framework are many fold.
Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for highly expensive satellite imagery.
Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared. For example, allowing different authors to compare results quantitatively.

The objective of such framework being:
\begin{enumerate}
\item To build, develop and validate statistical models for different stochastic processes that are inherent within the polarimetric SAR domain.
\item To allow easy, fast and repeatable simulations and experiments of various stochastic processes in designed, focused, as well as broad-based scenarios.
\item To allow easy application of different existing estimators as well as various transformations into focused and simulated scenarios as well as into practical real measured data.
\item To allow development and calculation of good performance indices for estimators. 
\item To allow visualization and analysis of the performance of different stochastic estimators.
\item Ultimately, to allow development of better and more accurate estimators, whose results can be verified: not only qualitatively on real life images, but also quantitatively through rigorous simulations.
\end{enumerate}

The possible benefits of this computational framework are:
\begin{enumerate}
\item Practical benefits
\begin{enumerate}
\item The computational frameworks allow for faster, quicker and more focused experiments. 
Often, a statistical hypothesis can be observed or rejected by designing and implementing an appropriate computational experiment.
\item The framework allows for easier analysis, and thus more insight to be gained, on the performance of an estimator. 
This, in turn, allows for design and development of better estimators.
\end{enumerate}
\item Academic benefits
\begin{enumerate}
\item The computational framework allows for quantitative evaluation and comparison of estimators.
With fast and repeated experiments, the framework allows one to not only compute a single performance value on a single experiment, but also to analyze the whole behaviour of such performance measures over repeated stochastic simulations.
\item Thus the computational framework provides significant help in deriving new performance evaluation criteria for statistical estimators.
\end{enumerate}
\end{enumerate}

\subsection{Data Collection}

This work has made extensive use of simulated data, which have a number of advantages listed below:
\begin{enumerate}
\item Once the model is validated against real-life data, simulated experiments can be carried out on more focused scenarios.
This allows smaller data sets to be generated and analysis can become faster and more accurate.
\item Contrary to real-life images where underlying coefficients are to be estimated, ground truth is readily available in simulated experiments.
\item Quantitative evaluation is possible not only via a single experiment on a single real-image but via repeated stochastic runs. 
\item Thus not only single values of mean or mean-squared-error are to be evaluated. 
As the whole response PDF is available, statistical bias or heteroskedasticity can also be reported.
\end{enumerate}

Besides simulated  data, we have gathered a large amount of real-life data.
Table \ref{tbl:collected_data} lists data made available to us, courtesy of EADS Innovation Works Singapore.

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Radar Platform & Polarization Mode & Data Capture Time \\
\hline
RadarSat 2 & Full Quad Pol & 29 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 05 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 12 Mar 2009 \\
RadarSat 2 & Full Quad Pol & 23 Jan 2009 \\
RadarSat 2 & Full Quad Pol & 30 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 06 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 19 Oct 2008 \\
RadarSat 2 & Full Quad Pol & 12 Nov 2008 \\
RadarSat 2 & Full Quad Pol & 25 Sep 2008 \\
TerraSar-X & Dual Pol (HH-VV) & 18 Apr 2008 \\
NASA-JPL AirSar & Full Quad Pol & 2001 \\
\hline
\end{tabular}
\caption{Collected imagery data}
\label{tbl:collected_data}
\end{table}

\subsection{Result Interpretation and Evaluation}

%How do you evaluate your solution? 
The
                achievement of the research objectives stated above not only provides
                novel solutions to the stated problem, it also
                illustrates the advantages and beneficial implications
                of the proposed theory.  
Compared
                to existing published techniques, the advantage of the
                proposed theory is qualitative, which does not require
                direct quantitative comparisons.
Instead
                a straightforward binary evaluation would be sufficient.
For
                the POLSAR scalar model, its advantages are that not
                only does it lead to consistent discrimination measures, it
                also generalizes the traditional model for one
                dimensional SAR intensity.
For
                the homoskedastic models, their advantage is that they
                enable an additive and homoskedastic statistical
                framework, which is not only capable of overcome various
                negative impacts of heteroskedasticity, but also results
                in a single better evaluation criteria that can combine
                and represent many different existing performance
                criteria.

To validate the theoretical models,  real-life data are used in this work.
Specifically, estimated theoretical PDFs are plotted against the histogram of real data,
  and a good visual match indicates a good validation.
In cases where theoretical PDF cannot be derived, simulated data are then generated
  and their histograms are matched against real-life practical data for validation.

%***IVM This was all said before...
%Simulated experiments allows evaluation of estimators against ground-truth.
%Errors can be quantitatively analyzed and methods to reduce such errors can be developed.
%Thus simulated experiments could produce quick results, which may provide faster analysis and 
%further insights for developing more accurate estimators.
